Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-02-03 paper/ms.tex
new changes

We generate a series of models ${\mathcal M}$ with different input parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$. We explore a wide range of values in the parameter space as follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30 different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to $\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$ takes 100 different values from $0.01$ to $1.00$ regularly spaced by $0.01$. In total the number of different sets of input parameters to be explored is $30 \times 30\times 100 = 290000$.

For each model we generate the number density distributions in three different ways as described in the previous section. For each volume we project along the $z$ direction and calculate its surface number density in units of sources per arcmin$^{2}$. For each number density distributionwe perform a Kolmogorov-Smirnov test to compare it against the $12$ observational values. From this test we obtain the value $0<P<1$ to reject the null hypothesis that the two data sets come from the same distribution. In this paper we use values of $P<0.1$ to consider that the simulated and observed number densities do not come from the same distributions.

Summarizing, for each model $M_{\rm min}, M_{\rm max}, f_{\rm occ}$, there are three different ways to calculate a KS test, which is in turn used to select the models that best reproduce the observations: from the full 210 mock sample, from 20 boot-strapped sets of 12 catalogs and finally from the same kind of boot-strapped catalogs that take into account the correlation in neighboughring observed fields.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.00\linewidth,angle=0]{./plots/cum_halos_tex.png}
\caption{ \label{figure:laes_dist} Cumulative mass function of dark matter haloes in the $210$ sub-volumes of $46\times 35\times 41$ $h^{-3}Mpc^{3}$. The variation in the total number of dark matter halos per sub-volume  evidences the effect of cosmic variance at such sub-volume scale. It is also appreciable the low population $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with $log(M/M_{\odot})>12.0$}.
\end{center} 
\end{figure}

\subsection{General Constraints on the Occupation Fraction}
The number density of dark matter halos per unit comoving volume is a well defined quantity for a given cosmological model, modulo the effects introduced by cosmic variance. The occupation fraction $f_{\rm occ}$ acts a renormalization factor of the halo number density to match the observational constrain of the surface density of LAEs.

In Fig. 1 we show the cumulative mass function of dark matter haloes in the $210$ sub-volumes extracted from the Bolshoi simulation. This mass function is expressed as a surface density by projecting the positions of all haloes along the $z$ direction and taking the surface of the rectangle in the $x$-$y$ plane as the nominal $880$ arcmin$^{2}$ we calculated in \S\ref{subsec:mocks}. The same figure shows as a vertical band the range of observed surface density of LAEs.

There is a characteristic halo mass $M_{\rm c}$ above which the halo mass functions are below the observational constraint, meaning that models with model parameters $I=\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ with $M_{\rm min}> M_{\rm c}$ have a number densiy that is already lower than the observational one, regardless of the value of $f_{\rm occ}$. Conversely, below for models with $M_{\rm min}<M_{\rm c}$ have a possibility of success if the occupation fraction $f_{\rm occ}$ is tuned as to lower the halo number density down to the observed value.

For the reasons explained above, the occupation fraction $f_{\rm occ}$ has a strong dependence on the mass parameters of the model $M_{\rm min}$ and $M_{\rm max}$. This allows us to focus in presenting the results of the best models in terms of these two parameters, knowing that the occupation fraction is already tightly constrained.

\subsection{Likelihood landscapes}

Figure \label{figure:landscape} presents the probability from the KS-tests that the observed and simulated surface densities can be considered as comming from similar distributions. For the reasons explained in the last section, we only show the results in the $M_{\rm min}-M_{\rm max}$ plane. The first panel show the results comming from using all the $210$ mocks for each model, the second and third panel from the boot-strapping of spatially uncorrelated and correlated fields, respectively.

\begin{figure}
\begin{center}
\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
\end{center} 
\caption{ \label{figure:landscape} 
}
\end{figure}

@@

>>>>

We generate a series of models ${\mathcal M}$ with different input parameters$\{M_{\rm min}, M_{\rm max}, f_{\rm occ}\}$ as follows. $M_{\rm min}$ and $M_{\rm max}$ are allowed to take 30 different values evenly spaced by $0.1$ dex, $M_{\rm min}$ ranges from $\log_{10}M_{\rm min}=10.0$ up to $\log_{10}M_{\rm min}=12.9$, while $M_{\rm max}$ range  from $\log_{10}M_{\rm min}=10.1$ up to $\log_{10}M_{\rm min}=13.0$. The occupation fraction $f_{\rm occ}$ takes 100 different values from $0.01$ to $1.00$ regularly spaced by $0.01$. In total the number of different sets of input parameters to be explored is $30 \times 30\times 100 = 290000$.

For each model ${\mathcal M}$ we compute the LAE surface density distributions for the three different ways of grouping the mock fields, as described in the previous section. For each sub-volume we project the positions of the LAE hosting halos along the $z$ direction and calculate its surface number density in units of sources per arcmin$^{2}$. For each number density distribution we perform a Kolmogorov-Smirnov againsg the $12$ surface density observational values. From this test we obtain the value $0<P<1$ to reject the null hypothesis, namely that the two data sets come from the same distribution. In this paper we use values of $P>0.1$ to consider that the simulated and observed number densities come from the same distribution.

@@

\begin{figure}
\begin{center}
%\includegraphics[width=1.00\linewidth,angle=0]{./plots/cum_halos_tex.png}
\caption{ \label{figure:laes_dist} Cumulative mass function of dark matter haloes in the $210$ sub-volumes of $46\times 35\times 41$ $h^{-3}Mpc^{3}$. The variation in the total number of dark matter halos per sub-volume  evidences the effect of cosmic variance at such sub-volume scale. It is also appreciable the low population $\lesssim10^{-3}h^{2}Mpc^{-2}$ of halos with $log(M/M_{\odot})>12.0$}.
\end{center} 
\end{figure}

\subsection{Dark Matter Halo Number Density}
... We comment first on the intergrated dark matter halo surface density as a function of mass for each one o the 210 sub-volumes in the Bolshoi simulation. This will allows us to better understand the expected trends for the LAEs preferred mass and the occupation fraction. Figure \ref{fig:laes_dist} show these distributions.

The shadowed region in Figure \ref{fig:laes_dist} shows the surface density values allowed by the observations. This figure tells us by inspection which model parameters cannot reproduce the observations. The regions where the DM surface density values are below the observational constraint correspond to high masses. For a model ${\mathcal M}$ with a minimum mass in this high mass range, the observations present a surface density to high to be possible achieved.

Conversely the regions where the halo surface density is higher than the observational constraints correspond to models ${\mathcal M}$ with a minimum mass below this threshold. Models with this minimum mass hava a chance for successfuly reproducing observations if the occupation fraction $f_{\rm occ}<1$ is tuned as to lower the halo number density down to the observed value.

@@

Figure \label{figure:landscape} presents the regions in the parameter space $M_{\rm min}-M_{\rm max}$ where the KS test yields values of $P>0.1$. Each panel corresponds to the three different ways of grouping the mock fields. In the case of the methods {\tt{MatchObs}} and {\tt{RandomObs}} the color code indicates the fraction of these 15 mock surveys with with $P>0.1$. The third panel shows the result for the method {\tt{FullVolume}}, in this case the color code correspond to the value of $P$ for a given model.

\begin{figure}
\begin{center}
%\includegraphics[width=1.00\linewidth,angle=0]{./plots/probabillity_contour06-10bar.png}
\end{center} 
\caption{ \label{figure:landscape} 
}
\end{figure}
